---
title: "flps"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{flps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = F,
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(flps)
```

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/flps)](https://CRAN.R-project.org/package=flps)
<!-- badges: end -->



## Fully Latent Principal Stratification (FLPS)

Fully Latent Principal Stratification (**FLPS**) is an extension of principal stratification.

## Install

Install the latest release from CRAN:

```{r}
devtools::install_github("sooyongl/flps")
```

The documentation is available at [here](https://sooyongl.github.io/flps/).

If compiling errors occur, see [here](https://github.com/stan-dev/rstan/wiki/Configuring-C---Toolchain-for-Windows#r-42).


## Basic working example

### Running with the package

- Generate a simulated rectangular data.
- This data will be converted to a list of data for [`rstan`](https://github.com/stan-dev/rstan) package.
- For latent variable models, Rasch, 2PL, GRM, and SEM (one-factor CFA) are available.


```{r eval = T}
inp_data <- flps::makeInpData(
  N       = 200,  # sample size
  R2Y     = 0.2,  # r^2 of outcome
  R2eta   = 0.5,  # r^2 of eta by one covariates
  omega   = 0.2,  # the effect of eta
  tau0    = 0.13, # direct effect
  tau1    = -0.06,# interaction effect between Z and eta
  lambda  = 0.8,  # the proportion of administered items
  nitem    = 10,   # the total number of items
  nfac    = 1,    # the number of latent factors
  lvmodel = 'rasch' # tag for latent variable model; case-sensitive (use lower-case letters)
)


```

`makeInpData()` creates input data for running FLPS.

- `inp_data`: a data frame containing all the data for FLPS. It is used in `runFLPS` function.

```{r eval = T}
# Input data matrix
data.table::data.table(inp_data)
```



- Fit your FLPS model

Now, provide information about your model. `runFLPS` internally coverts `inp_data` into the data format for `rstan` given the information, and runs FLPS.

To avoid having to compile the Stan code every time you run it, you can pre-compile the code using the `modelBuilder()` function along with the relevant measurement model. This function will compile the Stan code and store the resulting stanmodel object in the `flps` package directory. The next time you run `runFLPS()`, the code will skip the compilation step, making your analysis faster and more efficient. Otherwise, it will take a while for `runFLPS()` to compile the Stan code.

```{r}
modelBuilder(type = "rasch")
```


```{r eval = T}
res <- runFLPS(
  inp_data = inp_data,
  outcome = "Y",
  group = "Z",
  covariate = c("X"),
  lv_type = "rasch",
  lv_model = "F =~ v1 + v2 + v3 + v4 + v5 + v6 + v7 + v8 + v9 + v10",
  stan_options = list(iter = 1000, warmup = 500, cores = 1, chains = 2)
)
```


The summary of results can be shown by `summary()`.

```{r eval = T}

summary(res, type = "casual")

```


The `flps_causal()` shows the plot for the principal effects.

```{r eval = T}

flps_causal(res)

```




